\documentclass[10pt]{article}

% --- PACKAGES ---
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage[a4paper,margin=0.48in,top=0.42in,bottom=0.42in,left=0.52in,right=0.52in]{geometry}
\usepackage{lmodern}
\usepackage{microtype}
\usepackage{hyperref}
\usepackage{enumitem}
\usepackage{ragged2e}
\usepackage{array}

\pagestyle{empty}
\setlength{\parindent}{0pt}
\setlength{\parskip}{0pt}
\linespread{1}
\RaggedRight
\setlength{\tabcolsep}{0pt}
\setlength{\emergencystretch}{1.5em}
\raggedbottom

% --- SECTION HEADING ---
\newcommand{\resumesection}[1]{%
  \vspace{1.0ex}
  \noindent{\large\scshape #1}\par
  \vspace{0.5ex}
  \hrule height 0.35pt
  \vspace{1.0ex}
}

% --- ENTRY COMMANDS ---
\newcommand{\resumeentry}[4]{%
  \item[]
  \begin{tabular*}{\textwidth}{@{\extracolsep{\fill}}p{0.78\textwidth}r}
    {\textbf{#1}} & {#2} \\
    {\textit{#3}} & {\textit{#4}} \\
  \end{tabular*}
  \vspace{-0.8ex}
}

\newcommand{\resumesubentry}[2]{%
  \item[] {\textbf{#1}} \\
  \textit{#2} \\
  \vspace{-0.35ex}
}

% --- HYPERLINK COLORS ---
\hypersetup{%
    colorlinks=true,
    linkcolor=black,
    filecolor=black,
    urlcolor=black,
}

\setlist{nosep, topsep=0pt, parsep=0pt, itemsep=0pt, leftmargin=*, label={}}

% --- BEGIN DOCUMENT ---
\begin{document}
\fontsize{9.2}{10.2}\selectfont

% --- HEADER ---
\begin{center}
    \vspace{-1.1em}
    {\LARGE \textbf{Anes Abd Almalek}}\\
    \vspace{0.15ex}
    {\small Constantine, Algeria}\\
    \vspace{0.2ex}
    {\small +213794972232 \;|\; \href{mailto:anes.abdelmalek@univ-constantine2.dz}{anes.abdelmalek@univ-constantine2.dz} \;|\; \href{https://github.com/GIt-BITu}{github.com/GIt-BITu}}
\end{center}

% --- EDUCATION ---
\resumesection{Education}
\begin{itemize}
    \resumeentry{University of Constantine 2}{2025 -- Present}{Master's in Software Engineering \& Intelligent Systems}{Constantine, Algeria}
    \resumeentry{University of Constantine 2}{Jun 2025}{Bachelor's in Software Engineering}{Constantine, Algeria}
\end{itemize}

\resumesection{Languages}
{\textbf{Arabic:} Native, \textbf{English:} Fluent, \textbf{French:} Intermediate}

% --- EXPERIENCE ---
\resumesection{Experience}
\begin{itemize}
    \resumeentry{Software Engineering Intern}{Mar 2026 -- May 2026}{SETRAM}{Constantine, Algeria}
    \begin{itemize}[leftmargin=1.15em,label=\textbullet]
        \item Deployed a document traceability platform in a finance department office, reducing workload by 85\%, eliminating manual checks entirely, and cutting information search time by 75\%.
        \item Authored a report proposing a software migration/update plan, a risk mitigation strategy, and a PCC automation tool proposal.
    \end{itemize}

    \resumeentry{AI Research Intern}{Nov 2025}{CRBt -- Center of Biotechnology Research}{Constantine, Algeria}
    \begin{itemize}[leftmargin=1.15em,label=\textbullet]
        \item Built a two-stage Vision Transformer pipeline to detect and classify white blood cells into 18 classes, achieving up to 98\% accuracy on select classes.
    \end{itemize}

    \resumeentry{Android Developer Intern}{Jan 2024 -- Aug 2024}{Maduo Studio}{Dubai, UAE}
    \begin{itemize}[leftmargin=1.15em,label=\textbullet]
        \item Designed Android UI/UX with Kotlin and Jetpack Compose for a fitness app.
        \item Built a juice customization feature enabling users to select ingredients prepared by the gym’s restaurant.
    \end{itemize}

    \resumeentry{Robotics Teacher \& Coach}{Jun 2024 -- Jun 2026}{AljazarieROBOTICS}{Constantine, Algeria}
    \begin{itemize}[leftmargin=1.15em,label=\textbullet]
        \item Delivered Python and robotics training to youth participants.
        \item Organized and mentored national teams for Codeavour Algeria and led Algeria's delegation to I-Fest Tunisia 2026.
        \item Supported AI/programming initiatives with the Ministry of Youth and Sport for their staff.
    \end{itemize}

    \resumeentry{Developer Member}{Jan 2024 -- Jun 2025}{Google Developers Group}{Constantine, Algeria}
    \begin{itemize}[leftmargin=1.15em,label=\textbullet]
        \item Developed and reviewed web authentication features; contributed to local developer training events.
    \end{itemize}

    \resumeentry{Hackathon Mentor}{Nov 2023}{DevFest Constantine}{Constantine, Algeria}
    \begin{itemize}[leftmargin=1.15em,label=\textbullet]
        \item Mentored 7–9 teams (28–35 participants) in fintech app design during the DevFest Hackathon.
        \item Handled technical setup, guidance and support to participants and event logistics.
    \end{itemize}

    \resumeentry{Contributor}{Feb 2023 -- Sep 2023}{Mozilla Campus Club}{Constantine, Algeria}
    \begin{itemize}[leftmargin=1.15em,label=\textbullet]
        \item Worked on Android, AI/ML, and Networking initiatives. Supported content creation and team collaboration.
    \end{itemize}
\end{itemize}

% --- SELECTED PROJECTS ---
\resumesection{Selected Projects}
\begin{itemize}
    \resumesubentry{Multi-platform Car Marketplace (React Native)}{
      Designed, built, and deployed a miltiplatforms production React Native car marketplace connecting Algerian customers with Chinese suppliers, now used by a real client.
    }

    \resumesubentry{Grep Clone -- Custom Regex Engine (Java)}{
      Reimplemented grep from scratch, including a custom recursive-descent regex engine (quantifiers, groups, alternation, backreferences) built without Java's built-in regex library.
    }

    \resumesubentry{Git Clone -- Version Control Internals (C++)}{
      Currently building a from-scratch, dependency-free reimplementation of core Git internals in C++.
    }

    \resumesubentry{Python Automation Tool}{
      Automated downloading and organizing of 116 files from structured web archives using Selenium. Resolved race conditions and validated file completion integrity.
    }
\end{itemize}

% --- ACHIEVEMENTS ---
\resumesection{Achievements}
{\textit
Coached winning team to 2nd Place track 02 -- Codeavour Qatar (Junior Division), 2025\\
Directed Codeavour Algeria 2026 national operations\\
Mentored 2 of 5 winning teams (Track 1) -- Codeavour Jakarta (Global Finals), 2026\\
Completed the Skyscanner Software Engineering Job Simulation (Forage)\\
Taught 40+ students and mentored 100+ across national robotics and AI workshops
}

% --- TECHNICAL SKILLS ---
\resumesection{Technical Skills}
\begin{itemize}
\item[] \textbf{Languages:} Python, Java, Kotlin, JavaScript, C++, HTML/CSS, SQL, Bash.
\item[] \textbf{Frameworks/Tools:} Spring Boot, React, Django, Ktor, FastAPI, JavaFX, Selenium, Jetpack Compose, PostgreSQL, MySQL, Docker, Git, Linux, Hibernate, JPA, Figma, \LaTeX, Vim, JUnit, PyUnit, GitHub.
\item[] \textbf{Concepts:} REST APIs, OOP, Concurrency programming, Data Structures \& Algorithms, Networking, UML, Agile method, PEP8, Code Maintainability.
\end{itemize}

\end{document}